---
title: 'A Song of Ice and Fire'
author: "Samarth Patil"
output:
  html_document:
    df_print: paged
---

```{r warning = F}
suppressPackageStartupMessages({
  library(TSA)
  library(ggplot2)
  library(dplyr)
  library(forecast)
  library(tseries)
  library(lmtest)
  library(Metrics)
})

```

Wikipedia web visit (Sessions per day) was counted. Data were collected from 11.29.2015 to 11.28.2016 -- 366 days in total.

Loading the data and plotting it.
```{r}
wiki_data <- read.csv('./data/Wiki_A_Song_of_Ice_and_Fire_web_visit-3.txt', header=F)
sif=ts(wiki_data$V1)
ts.plot(sif)
```

Split the time series into a training set and a test set. 
We are interested in forecasting the web visit volume in the next 7 days.
So define the training set as the first 359 data points, and the test set as the last 7 data points.

```{r}
sif_train=ts(sif[1:359], start=1, end = 359)
sif_test=ts(sif[360:366], start=360, end=366)
```

Run the auto arima to see how it performs.
Roughly a coefficient is significant if its magnitude is at least twice as large as its standard error.

```{r}
arima0=auto.arima(sif_train)
arima0
coeftest(arima0)
```
All three coefficients are significant

Forecast the web visit volume in the next 7 days. 
Plot the forecasts, the raw data, and the 80\% and 95\% prediction intervals.
Our lowest expectation is that at least the 95\% prediction interval should cover the true data. Our highest expectation is that the forecasts highly align with the true data.

```{r}
arima0_forecast=forecast(arima0, h=7)
autoplot(arima0_forecast)+autolayer(sif_test, series="Data") +
  autolayer(arima0_forecast$mean, series="Forecasts")
```
The forecasts are acceptable, but not perfect, as we can see that it does not capture the trend. However, even the 80% confidence contains the true values. 


Calculate the RMSE of the forecasts. This RMSE will be used as a benchmark for comparison later.

```{r}
rmse_arima=rmse(arima0_forecast$mean,sif_test)
```

Create regressors.

```{r}
t1=1:359
t2=t1^2
t1_test=360:366
t2_test=t1_test^2

```

On the training set, run a linear regression using `sif` against both `t1` and `t2`. 


```{r}
lm0=lm(sif_train~t1+t2)
summary(lm0)

```
All coefficients are significant


Extrapolate the results to the test set and plot them.

```{r}
X_test=data.frame(t1=t1_test, t2=t2_test)
lm0_forecast=forecast(lm0,newdata = X_test)
lm0_forecast=ts(lm0_forecast$mean,start = 360,end = 366)
lm0_forecast

```


Calculate the RMSE on the test set for the linear model above.

```{r}
rmse_lm=rmse(lm0_forecast,sif_test)
```

Extract the residuals of the linear model above. Consider it as a new time series for Arima. 
Plot the residuals and compare the curve with the one above.


```{r}
z=ts(lm0$residuals, start = 1, end = 359)
ts.plot(z, ylab = "Linear Model Residuals", col='orange')
lines(sif)
```

Run an `auto.arima()` on the residuals, and calculate the forecasts on the test set.

```{r}
arima1=auto.arima(z)
z_forecast=forecast(arima1, h=7)
coeftest(arima1)
```

Now calculate the forecasts combining both the linear model and the ARIMA, and plot the results from all three models (i.e., arima alone, linear model alone, linear model plus arima)

```{r}
y_forecast=lm0_forecast+z_forecast$mean
ts.plot(sif_test)
lines(y_forecast, col='blue')
lines(arima0_forecast$mean, col='green')
lines(lm0_forecast, col='red')
```


Now calculate the RMSE on the test set for the linear model plus arima above.
```{r}
rmse_lm_plus_arima=rmse(y_forecast,sif_test) 
```
rmse_lm_plus_arima is lower than both rmse_lm and rmse_arima


Fine-tune the model

```{r}
for(i in 1:10){
  for( j in 1:10){
    arima2=Arima(z,order=c(i,1,j), method="ML")  
    z_forecast1=forecast(arima2, h=7)
    y_forecast1=lm0_forecast+z_forecast1$mean
    rmse_lm_plus_your_arima=rmse(y_forecast1,sif_test)
    if(rmse_lm_plus_your_arima < 400){
      print(paste0(rmse_lm_plus_your_arima,'-',i,'-',j))
    }
  }
}
```
arima(7,1,8) and arima(8,1,10) both beat the result above by over 10% in terms of RMSE

